---
output:
  prettydoc::html_pretty:
    theme: tactile
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
[League Homepage](https://fantasy.espn.com/baseball/league?leagueId=62615350){style="float:right"}
<br>
[History](#anchor8){style="float:right"}
[Scoring-](#anchor6){style="float:right"}
[Awards-](#anchor4){style="float:right"}
[Trends-](#anchor3){style="float:right"}
[Results-](#anchor2){style="float:right"}
[Standings-](#anchor1){style="float:right"}
[Rules-](#anchor7){style="float:right"}

<br>

<center>
# **The Bryan Reynolds Fan Club** {#anchor5}
### Phi Kappa Psi-Illinois Delta: Fantasy Baseball League
</center>

***

## **Rules** {#anchor7}

* Draft:
  + Snake-22 rounds
  + Draft order randomized an hour before the draft
  + 90 seconds per pick
  + Draft date/time: TBD
* Standings:
  + Three Divisions-6 Teams per division
  + Victory Points (VP):
    + Winning your weekly matchup=2 VP
    + Top 6 in total points for the week=2 VP
    + Middle 6 in total points for the week=1 VP
* Schedule: 
  + TBD depending on MLB schedule reconstruction after COVID-19
  + Most likely play everyone in division twice and play two other divisions equal amount
  + Each week starts Monday and goes through games on Sunday
* Rosters: 
  + Starting Rosters: C, 1B, 2B, SS, 3B, IF, 4 OF, 4 SP, and 2 RP
  + 5 Bench slots
  + 2 IR slots
  + Once a player plays for the week, they are locked in for the week
* Playoffs:
  + 6 teams make the playoffs
  + Best Record in each division are top 3 seeds
    + Tiebreakers: 
      1. VP
      2. Adjusted Record (what your record would be if you played everyone every week)
      3. Total Points For
    + They are ranked 1-3 by VP
      + 1 and 2 get a first round bye
  + 3 Wild Card slots are based on most VP to not win a division
    + Tiebreakers: 
      1. Adjusted Record (what your record would be if you played everyone every week)
      2. Total Points For
  + 2 weeks per playoff round
* Waivers: 
  + $100 free agent budget for the season
  + Minimum bid of $1
  + Waivers go through at Noon (central time) on Sunday
* Side Pots: 
  + Team with the most total points for the week wins the designated side pot amount
  + Side pot $ amount is the same for every week
  + Side pot only active during regular season
  
***

<br>

## **Standings** {#anchor1}

### *The Berty Bunch*
|Team|Owner|Record|Victory Points|Adjusted Record|Points For   |Points Against|
|---|---|---|---|---|---|---|
|Team Chiganos   |Sam Chiganos   |0-0   |0   |0-0   |0   |0   |
|Padre Passion   |Maxx Wayne   |0-0   |0   |0-0   |0   |0   |
|Team Kane   |Mike Kane   |0-0   |0   |0-0   |0   |0   |
|Alec's Team Alec   |Alec Campbell   |0-0   |0   |0-0   |0   |0   |
|Aang Iceberg Ass   |Rapha Siordia   |0-0   |0   |0-0   |0   |0   |
|Team Wong   |Eric jung   |0-0   |0   |0-0   |0   |0   |


### *22's Divison*
|Team|Owner|Record|Victory Points|Adjusted Record|Points For   |Points Against|
|---|---|---|---|---|---|---|
|Team Joauquin   |Anthony Walsh   |0-0   |0   |0-0   |0   |0   |
|Team Pellikan   |TJ Pellikan   |0-0   |0   |0-0   |0   |0   |
|Team Ray   |Charlie Ray   |0-0   |0   |0-0   |0   |0   |
|Team Garcia   |Alex Garcia   |0-0   |0   |0-0   |0   |0   |
|Team Farnan   |Bobby Farnan   |0-0   |0   |0-0   |0   |0   |
|Team CrookedB   |Brennan Hartigan   |0-0   |0   |0-0   |0   |0|


### *Salen's Disciples*
|Team   |Owner   |Record   |Victory Points   |Adjusted Record   |Points For   |Points Against   |
|---|---|---|---|---|---|---|
|Team Culp   |Grant Lee Culp   |0-0   |0   |0-0   |0   |0   |
|Cubs 2019   |John Postlethwait   |0-0   |0   |0-0   |0   |0   |
|Team Deuter   |Alec Deuter   |0-0   |0   |0-0   |0   |0   |
|Team Hume   |Joe Hume   |0-0   |0   |0-0   |0   |0   |
|Team Salen   |Brian Metzger   |0-0   |0   |0-0   |0   |0   |
|Team Skiles   |Aidan Skiles   |0-0   |0   |0-0   |0   |0   |

### *Inter-Division/Wild Card*
|Place   |Team   |Owner   |Victory Points   |Adjusted Record   |Total Points For   |
|---|---|---|---|---|---|
|1   |   |   |   |   |   |
|2  |   |   |   |   |   |
|3   |   |   |   |   |   |
|4   |   |   |   |   |   |
|5   |   |   |   |   |   |
|6   |   |   |   |   |   |
|7   |   |   |   |   |   |
|8   |   |   |   |   |   |
|9   |   |   |   |   |   |
|10   |   |   |   |   |   |
|11   |   |   |   |   |   |
|12   |   |   |   |   |   |
|13   |   |   |   |   |   |
|14   |   |   |   |   |   |
|15   |   |   |   |   |   |
|16   |   |   |   |   |   |
|17   |   |   |   |   |   |
|18   |   |   |   |   |   |

***
<br>

## **Results** {#anchor2}
##### [League Scoreboard](https://fantasy.espn.com/baseball/league/scoreboard?leagueId=62615350)
### *Top Scorers By Week*
##### Week 1: Team-... Hitter-... Pitcher-...
##### Week 2: Team-... Hitter-... Pitcher-...
##### Week 3: Team-... Hitter-... Pitcher-...
##### Week 4: Team-... Hitter-... Pitcher-...
##### Week 6: Team-... Hitter-... Pitcher-...
##### Week 7: Team-... Hitter-... Pitcher-...
##### Week 8: Team-... Hitter-... Pitcher-...
##### Week 9: Team-... Hitter-... Pitcher-...
##### Week 10: Team-... Hitter-... Pitcher-...

***
<br>

## **Trends** {#anchor3}

#### *Trending Up* &uarr;
|Team   |Owner   |Change in Playoff %   |Change in VP standings   | 
|---|---|---|---|
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |

#### *Trending Down* &darr;
|Team   |Owner   |Change in Playoff %|Change in VP standings   | 
|---|---|---|---|
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |

```{r include=FALSE}
everyone=c('Campbell','Chiganos','Jung','Kane','Siordia','Wayne','Farnan','Garcia','Hartigan','Pellikan','Ray','Walsh','Culp','Deuter','Hume','Metzger','Postlethwait','Skiles')
playoff_chance=c(rep(33.3,18))
victory_points=c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
division=c(rep(1,6),rep(2,6),rep(3,6))
total=data.frame(everyone,playoff_chance,victory_points,division)
```

```{r echo=FALSE}
plot(total$victory_points,total$playoff_chance,pch=total$division,xlim=c(0,20),ylim=c(0,100),xlab='Victory Points',ylab='Playoff Percentage')
```

***
<br>

## **Awards** {#anchor4}

#### *Owner Awards*
|Award   |2019   |2020   |
|---|---|---|
|Champion   |TJ Pellikan   |   |
|2nd Place   |Rapha Siordia   |   |
|3rd Place   |Charlie Ray   |   |
|4th Place   |Anthony Walsh   |   |
|Mr. Irrelevant   |Jackson Spencer   |   |
|Regular Season MVP   |Charlie Ray (9286.3 points)   |   |
|Benchwarmer   |Jon Starr (6678 points)   |   |
|The Black Cat   |Brian Metzger (8346.5 points against)   |   |
|The Luck of the Irish   |Jon Starr (7407 points against)   |   |
|Longest Winning Streak   |John Postlethwait (8)   |   |
|Longest Losing Streak   |John Postlethwait (9)   |   |
|Biggest Tweak   |TJ Pellikan (38 transactions)   |   |
|Ghost   |Grant Lee Culp and Brian Metzger (1 transaction)   |   |
|Barry Bonds   |TJ Pellikan (639 HR)   |   |
|Fundamental Baseball   |Maxx Wayne (1101 1B)   |   |
|Moneyball   |TJ Pellikan (639 BB batting)   |   |
|Adam Dunn   |Bobby Farnan (1374 K batting)   |   |
|Rickey Henderson   |Jon Starr (125 SB)   |   |
|Innings Eater   |Maxx Wayne (977 IP)   |   |
|Nolan Ryan   |Maxx Wayne (937 K pitching)   |   |
|Cy Young   |Maxx Wayne (69 W)  |   |
|Kinda Also Cy Young   |TJ Pellikan (54 L)   |   |
|Mike Soroka   |Bobby Farnan (3.133 ERA)   |   |
|Trevor Hoffman   |Brian Metzger (63 S)   |   |
|Biggest Choker    |Brian Metzger (13 BS)   |   |
|Matt Thornton   |Alec Deuter (44 H)   |   |

#### *Player Awards*
|Award   |2019   |2020   |
|---|---|---|
|1st/2nd Round Bust   |Corey Kluber (Mike Kane)   |   |
|Early Bust (Rounds 3-5)   |Miguel Andujar (Maxx Wayne)   |   |
|Mid Sleeper (Rounds 10-17)   |DJ LeMahieu (Charlie Ray)  |   |
|Deep Sleeper (Rounds 18-22)   |Kolten Wong (Alec Campbell)   |   |
|Best Waiver Add   |Pete Alonso (TJ Pellikan)   |   |

***
<br>

## **Scoring** {#anchor6}

```{r include=FALSE}
Batting_Stat=c('H','R','1B','2B','3B','HR','RBI','GWRBI','BB','IBB','K','SAC','SB','CS','GIDP','CYCLE','GSHR',' ',' ')
Batting_Points=c(1,3,1,2,3,4,3,3,1,1,-1,2,1,-1,-4,25,5,' ',' ')
batt=data.frame(Batting_Stat,Batting_Points)
Pitching_Stat=c('IP','H','ER','HR','BB','K','WP','B','Pickoff','QS','CG','SO','No Hitter','Perfect Game','W','L','SV','BS','Hold' )
Pitching_Points=c(3,-.5,-1.5,-2,-.5,1,-1,-1,5,12,20,35,75,100,3,-3,12,-6,10)
pitch=data.frame(Pitching_Stat,Pitching_Points)
Fielding_Stat=c('Put Out','Assist','Outfield Assist','Error','Double Play Turned',rep(' ',14))
Fielding_Points=c(.2,.5,10,-5,2,rep(' ',14))
field=data.frame(Fielding_Stat,Fielding_Points)
all=data.frame(batt,pitch,field)
```

```{r echo=FALSE}
knitr::kable(all,col.names=c('Batting Stats','Points','Pitching Stats','Points','Fielding Stats','Points'))
```

***

##  **History** {#anchor8}

### *All time Standings*

```{r include=FALSE}
names=c('TJ Pellikan','Rapha Siordia','Charlie Ray','Anthony Walsh','Brennan Hartigan','Bobby Farnan','Maxx Wayne','Grant Culp','John Postlethwait','Alec Campbell','Alex Garcia','Alec Deuter','Jon Starr','Mike Kane','Brian Metzger','Jackson Spencer','Sam Chiganos','Eric Jung','Aidan Skiles','Joe Hume')
win_percent=round(c(12/17,12/17,13/17,12/17,11/17,11/17,9/17,8/16,8/17,8/17,8/17,7/16,6/17,4/17,3/17,3/17,rep(0,4)),2)
records=c('12-5','12-5','13-4','12-5','11-6','11-6','9-8','8-8-1','8-9','8-9','8-9','7-9-1','6-11','4-13','3-14','3-14',rep('0-0',4))
finish=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,rep(0,4))
playoff_percent=round(c(3/3,2/3,1/2,0/2,0/1,0/1,rep(0,14)),2)
playoff_record=c('3-0','2-1','1-1','0-2','0-1','0-1',rep('0-0',14))
top_4=c(1,1,1,1,rep(0,16))
champ_appear=c(1,1,rep(0,18))
champ=c(1,rep(0,19))
best_finish=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,rep(0,4))
playoff_appear=c(1,1,1,1,1,1,rep(0,14))
division_titles=c(0,0,1,rep(0,17))
awards=c(6,1,3,1,0,2,5,1,2,1,0,1,3,1,3,0,rep(0,4))
avg_pf=c(5,3,1,2,6,4,8,10,7,12,13,9,16,14,11,15,rep(0,4))
avg_pa=c(14,8,6,9,2,13,11,10,7,15,12,3,16,5,1,4,rep(0,4))
diff=c(41.6,56.9,81.5,62.5,-13.6,57.1,17.8,-12.1,11.8,-5.1,-28.8,-27.7,-42.9,-57.9,-48.2,-93,rep(0,4))
long_win=c(5,4,4,5,3,6,3,3,8,2,3,2,3,1,1,2,rep(0,4))
long_lose=c(1,1,1,2,2,3,22,9,3,3,3,4,4,7,8,rep(0,4))

history=data.frame(cbind(names,finish,best_finish,win_percent,records,playoff_percent,playoff_record,playoff_appear,top_4,champ_appear,champ,division_titles,avg_pf,avg_pa,diff,long_win,long_lose,awards))
```

```{r echo=FALSE}
knitr::kable(history,col.names=c('Owner','Average Finish','Best Finish','Win Percentage','Record','Playoff Win Percentage','Playoff Record','Playoff Appearances','Top 4 Finishes','Championship Appearances','Championships','Division Titles','Average Points For Rank','Average Points Against Rank','Average Point Differential','Longest Win Streak','Longest Lose Streak','Awards'))
```

### *2019 Standings*

```{r include =FALSE}
names0=c('TJ Pellikan','Rapha Siordia','Charlie Ray','Anthony Walsh','Brennan Hartigan','Bobby Farnan','Maxx Wayne','Grant Culp','John Postlethwait','Alec Campbell','Alex Garcia','Alec Deuter','Jon Starr','Mike Kane','Brian Metzger','Jackson Spencer')
win_percent0=round(c(12/17,12/17,13/17,12/17,11/17,11/17,9/17,8/16,8/17,8/17,8/17,7/16,6/17,4/17,3/17,3/17),2)
records0=c('12-5','12-5','13-4','12-5','11-6','11-6','9-8','8-8-1','8-9','8-9','8-9','7-9-1','6-11','4-13','3-14','3-14')
finish0=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)
playoff_percent0=round(c(3/3,2/3,1/2,0/2,0/1,0/1,rep(0,10)),2)
playoff_record0=c('3-0','2-1','1-1','0-2','0-1','0-1',rep('0-0',10))
playoff_appear0=c(rep('Yes',6),rep('No',10))
division_titles0=c('No','No','Everyone Combined',rep('No',13))
awards0=c(6,1,3,1,0,2,5,1,2,1,0,1,3,1,3,0)
avg_pf0=c(8265.75,8843.75,9286.25,8846.25,8098.75,8606,8025.75,7565.75,8087,7374.25,7206,7809.75,6678,7174.25,7526.75,6696)
avg_pa0=c(7559,7877,7900.25,7783,8329.5,7634.5,7723.25,7771.25,7886.75,7461.5,7695,8280.5,7407,8158.25,8346.5,8277)
diff0=c(41.6,56.9,81.5,62.5,-13.6,57.1,17.8,-12.1,11.8,-5.1,-28.8,-27.7,-42.9,-57.9,-48.2,-93)
long_win0=c(5,4,4,5,3,6,3,3,8,2,3,2,3,1,1,2)
long_lose0=c(1,1,1,2,2,3,22,9,3,3,3,4,4,7,8)

twenty_nineteen=data.frame(cbind(finish0,names0,win_percent0,records0,playoff_appear0,playoff_percent0,playoff_record0,division_titles0,avg_pf0,avg_pa0,diff0,long_win0,long_lose0,awards0))
```

```{r echo=FALSE}
knitr::kable(twenty_nineteen,col.names=c('Place','Owner','Win Percentage','Record','Playoffs','Playoff Win Percentage','Playoff Record','Division Champ','Points For','Points Against','Point Differential','Longest Win Streak','Longest Lose Streak','Awards'))
```

***



[Top of Page](#anchor5)

Site created by: Maxx Wayne

Last Updated: 5/30/2020

