---
output:
  prettydoc::html_pretty:
    theme: tactile
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
[League Homepage](https://fantasy.espn.com/baseball/league?leagueId=62615350){style="float:right"}
<br>
[Scoring](#anchor6){style="float:right"}
[Awards-](#anchor4){style="float:right"}
[Trends-](#anchor3){style="float:right"}
[Results-](#anchor2){style="float:right"}
[Standings-](#anchor1){style="float:right"}

<br>

<center>
# **The Bryan Reynolds Fan Club** {#anchor5}
### Phi Kappa Psi-Illinois Delta: Fantasy Baseball League
</center>

***

## **Standings** {#anchor1}

### *21's Divison*
|Team|Owner|Record|Victory Points|Adjusted Record|Points For   |Points Against|
|---|---|---|---|---|---|---|
|Team Chiganos   |Sam Chiganos   |0-0   |0   |0-0   |0   |0   |
|Padre Passion   |Maxx Wayne   |0-0   |0   |0-0   |0   |0   |
|Team Kane   |Mike Kane   |0-0   |0   |0-0   |0   |0   |
|Alec's Team Alec   |Alec Campbell   |0-0   |0   |0-0   |0   |0   |
|Aang Iceberg Ass   |Rapha Siordia   |0-0   |0   |0-0   |0   |0   |
|Team Wong   |Eric jung   |0-0   |0   |0-0   |0   |0   |


### *22's Divison*
|Team|Owner|Record|Victory Points|Adjusted Record|Points For   |Points Against|
|---|---|---|---|---|---|---|
|Team Joauquin   |Anthony Walsh   |0-0   |0   |0-0   |0   |0   |
|Team Pellikan   |TJ Pellikan   |0-0   |0   |0-0   |0   |0   |
|Team Ray   |Charlie Ray   |0-0   |0   |0-0   |0   |0   |
|Team Garcia   |Alex Garcia   |0-0   |0   |0-0   |0   |0   |
|Team Farnan   |Bobby Farnan   |0-0   |0   |0-0   |0   |0   |
|Team CrookedB   |Brennan Hartigan   |0-0   |0   |0-0   |0   |0|


### *Mixed Division*
|Team   |Owner   |Record   |Victory Points   |Adjusted Record   |Points For   |Points Against   |
|---|---|---|---|---|---|---|
|Team Culp   |Grant Lee Culp   |0-0   |0   |0-0   |0   |0   |
|Cubs 2019   |John Postlethwait   |0-0   |0   |0-0   |0   |0   |
|Team Deuter   |Alec Deuter   |0-0   |0   |0-0   |0   |0   |
|Team Hume   |Joe Hume   |0-0   |0   |0-0   |0   |0   |
|Team Salen   |Brian Metzger   |0-0   |0   |0-0   |0   |0   |
|Team Skiles   |Aidan Skiles   |0-0   |0   |0-0   |0   |0   |

### *Inter-Division/Wild Card*
|Place   |Team   |Owner   |Victory Points   |Adjusted Record   |Total Points For   |
|---|---|---|---|---|---|
|1   |   |   |   |   |   |
|2  |   |   |   |   |   |
|3   |   |   |   |   |   |
|4   |   |   |   |   |   |
|5   |   |   |   |   |   |
|6   |   |   |   |   |   |
|7   |   |   |   |   |   |
|8   |   |   |   |   |   |
|9   |   |   |   |   |   |
|10   |   |   |   |   |   |
|11   |   |   |   |   |   |
|12   |   |   |   |   |   |
|13   |   |   |   |   |   |
|14   |   |   |   |   |   |
|15   |   |   |   |   |   |
|16   |   |   |   |   |   |
|17   |   |   |   |   |   |
|18   |   |   |   |   |   |

***
<br>

## **Results** {#anchor2}
##### [League Scoreboard](https://fantasy.espn.com/baseball/league/scoreboard?leagueId=62615350)
### *Top Scorers By Week*
##### Week 1: Team-... Hitter-... Pitcher-...
##### Week 2: Team-... Hitter-... Pitcher-...
##### Week 3: Team-... Hitter-... Pitcher-...
##### Week 4: Team-... Hitter-... Pitcher-...
##### Week 6: Team-... Hitter-... Pitcher-...
##### Week 7: Team-... Hitter-... Pitcher-...
##### Week 8: Team-... Hitter-... Pitcher-...
##### Week 9: Team-... Hitter-... Pitcher-...
##### Week 10: Team-... Hitter-... Pitcher-...

***
<br>

## **Trends** {#anchor3}

#### *Trending Up* &uarr;
|Team   |Owner   |Change in Playoff %   |Change in VP standings   | 
|---|---|---|---|
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |

#### *Trending Down* &darr;
|Team   |Owner   |Change in Playoff %|Change in VP standings   | 
|---|---|---|---|
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |

```{r include=FALSE}
everyone=c('Campbell','Chiganos','Jung','Kane','Siordia','Wayne','Farnan','Garcia','Hartigan','Pellikan','Ray','Walsh','Culp','Deuter','Hume','Metzger','Postlethwait','Skiles')
playoff_chance=c(1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3,1/3)
victory_points=c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
division=c(rep(1,6),rep(2,6),rep(3,6))
total=data.frame(everyone,playoff_chance,victory_points,division)
```

```{r echo=FALSE}
plot(total$victory_points,total$playoff_chance,pch=total$division,xlim=c(0,20),ylim=c(0,100),xlab='Victory Points',ylab='Playoff Percentage')
```

***
<br>

## **Awards** {#anchor4}

#### *Owner Awards*
|Award   |2019   |2020   |
|---|---|---|
|Champion   |TJ Pellikan   |   |
|2nd Place   |Rapha Siordia   |   |
|3rd Place   |Charlie Ray   |   |
|4th Place   |Anthony Walsh   |   |
|Regular Season MVP   |Charlie Ray (9286.3 points)   |   |
|Benchwarmer   |Jon Starr (6678 points)   |   |
|The Black Cat   |Brian Metzger (8346.5 points against)   |   |
|The Luck of the Irish   |Jon Starr (7407 points against)   |   |
|Biggest Tweak   |TJ Pellikan (38 transactions)   |   |
|Ghost   |Grant Lee Culp and Brian Metzger (1 transaction)   |   |
|Barry Bonds   |TJ Pellikan (639 HR)   |   |
|Fundamental Baseball   |Maxx Wayne (1101 1B)   |   |
|Moneyball   |TJ Pellikan (639 BB batting)   |   |
|Adam Dunn   |Bobby Farnan (1374 K batting)   |   |
|Rickey Henderson   |Jon Starr (125 SB)   |   |
|Innings Eater   |Maxx Wayne (977 IP)   |   |
|Nolan Ryan   |Maxx Wayne (937 K pitching)   |   |
|Cy Young   |Maxx Wayne (69 W)  |   |
|Kinda Also Cy Young   |TJ Pellikan (54 L)   |   |
|Mike Soroka   |Bobby Farnan (3.133 ERA)   |   |
|Trevor Hoffman   |Brian Metzger (63 S)   |   |
|Biggest Choker    |Brian Metzger (13 BS)   |   |
|Matt Thornton   |Alec Deuter (44 H)   |   |

#### *Player Awards*
|Award   |2019   |2020   |
|---|---|---|
|1st/2nd Round Bust   |Corey Kluber (Mike Kane)   |   |
|Early Bust (Rounds 3-5)   |Miguel Andujar (Maxx Wayne)   |   |
|Mid Sleeper (Rounds 10-17)   |DJ LeMahieu (Charlie Ray)  |   |
|Deep Sleeper (Rounds 18-22)   |Kolten Wong (Alec Campbell)   |   |
|Best Waiver Add   |Pete Alonso (TJ Pellikan)   |   |

***
<br>

## **Scoring** {#anchor6}

```{r include=FALSE}
Batting_Stat=c('H','R','1B','2B','3B','HR','RBI','GWRBI','BB','IBB','K','SAC','SB','CS','GIDP','CYCLE','GSHR',' ',' ')
Batting_Points=c(1,3,1,2,3,4,3,3,1,1,-1,2,1,-1,-4,25,5,' ',' ')
batt=data.frame(Batting_Stat,Batting_Points)
Pitching_Stat=c('IP','H','ER','HR','BB','K','WP','B','Pickoff','QS','CG','SO','No Hitter','Perfect Game','W','L','SV','BS','Hold' )
Pitching_Points=c(3,-.5,-1.5,-2,-.5,1,-1,-1,5,12,20,35,75,100,3,-3,12,-6,10)
pitch=data.frame(Pitching_Stat,Pitching_Points)
Fielding_Stat=c('Put Out','Assist','Outfield Assist','Error','Double Play Turned',rep(' ',14))
Fielding_Points=c(.2,.5,10,-5,2,rep(' ',14))
field=data.frame(Fielding_Stat,Fielding_Points)
all=data.frame(batt,pitch,field)
```

```{r echo=FALSE}
knitr::kable(all,col.names=c('Batting Stats','Points','Pitching Stats','Points','Fielding Stats','Points'))
```

***

[Top of Page](#anchor5)

Site created by: Maxx Wayne

Last Updated: 3/29/2020

