---
title: "Ryan Tannehill Fan Club"
output:
  prettydoc::html_pretty:
    theme: hpstr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
[Fantasy Leagues Homepage](https://maxxwayne.github.io/){style="float:right"}
<br>
[League Homepage](https://fantasy.espn.com/football/league?leagueId=21575912&pendingReactivation=true){style="float:right"}
<br>
[History](#anchor7){style="float:right"}
[Scoring-](#anchor6){style="float:right"}
[Awards-](#anchor5){style="float:right"}
[Trends-](#anchor4){style="float:right"}
[Results-](#anchor3){style="float:right"}
[Standings-](#anchor2){style="float:right"}
[Rules-](#anchor1){style="float:right"}

## **Rules** {#anchor1}

* **Draft:**
  + Auction-$200 budget
  + Draft order randomized an hour before the draft
  + 30 seconds to nominate
  + Draft date/time: TBD
* **Standings:**
  + One division
  + Victory Points (VP):
    + Winning your weekly matchup=2 VP
    + Top 5 in total points for the week=2 VP
    + Middle 5 in total points for the week=1 VP
* **Schedule:** 
  + 13 weeks
  + Play everyone once
* **Rosters:** 
  + Starting Rosters: QB, 2 RB, 2 WR, TE, 2 FLEX (RB/WR/TE), 1 individual defensive player
  + 5 Bench slots
  + 1 IR slots
  + Once a player plays for the week, they are locked in for the week
* **Playoffs:**
  + 6 teams make the playoffs
    + Criteria: 
      1. VP
      2. Adjusted Record (what your record would be if you played everyone every week)
      3. Record
      4. Head-to-head record
      5. Total Points For
    + 1 and 2 get a first round bye
  + 1 week per playoff round
* **Waivers:** 
  + $100 free agent budget for the season
  + Minimum bid of $1
  + Waivers go through at Noon (central time) on Wednesday
  + If a player is not claimed on waivers, they become a free agent
    + Free Agents are free and are "first come first serve"
* **Scoring:**
  + .5 PPR
  + See [scoring](#anchor6) tab for more details
* Side Pots: 
  + Team with the most total points for the week wins the designated side pot amount
  + Side pot $ amount is the same for every week
  + Side pot only active during regular season
  
***

<br>

## **Standings** {#anchor2}

```{r include=FALSE}
place=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14)
teams=c('2 Girls 1 Kupp','Team Littyville','Team No Cappin','Cuppers Da','Ditka in her Butkus','Chicago Khalil Big-Macs','Jerry Jones Sock','The Four Horsemen','Team Joergerbomb','Team Kittle',' ',' ',' ',' ')
owners=c('Trevor Corsello','John Postlethwait','Cole Nelsen','Rapha Siordia','Julian Hilpuesch','Max Mitchell','Jackson Spencer','Maxx Wayne','Javen Joerger','Brian Metzger',' ',' ',' ',' ')
vp=c(rep(0,14))
adj_record=c(rep('0-0',14))
record=c(rep('0-0',14))
points_for=c(rep(0,14))
points_ag=c(rep(0,14))
standings=data.frame(cbind(place,teams,owners,vp,adj_record,record,points_for,points_ag))
```

```{r echo=FALSE}
knitr::kable(standings,col.names=c('Place','Team','Owner','VP','Adjusted Record','Record','Points For','Points Against'))
```

***

<br>

## **Results** {#anchor3}
##### [League Scoreboard](https://fantasy.espn.com/football/league/scoreboard?leagueId=21575912)
### *Top Scores by Week*
```{r include=FALSE}
week=c('Week 1','Week 2','Week 3','Week 4','Week 5','Week 6','Week 7','Week 8','Week 9','Week 10','Week 11','Week 12','Week 13')
team=c(rep(' ',13))
qb=c(rep(' ',13))
rb=c(rep(' ',13))
wr=c(rep(' ',13))
te=c(rep(' ',13))
idp=c(rep(' ',13))
leaders=data.frame(cbind(week,team,qb,rb,wr,te,idp))
```

```{r echo=FALSE}
knitr::kable(leaders,col.names=c('Week','Team','QB','RB','WR','TE','Defensive Player'))
```

***

<br>

## **Trends** {#anchor4}
#### *Trending Up* &uarr;
|Team   |Owner   |Change in Playoff %   |Change in VP standings   | 
|---|---|---|---|
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |

#### *Trending Down* &darr;
|Team   |Owner   |Change in Playoff %|Change in VP standings   | 
|---|---|---|---|
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |
|n/a   |n/a   |0   |0   |

```{r include=FALSE}
library(ggplot2)
playoff_chance=round(c(rep((6/14)*100,14)),2)
trend=data.frame(cbind(owners,vp,playoff_chance))
```

```{r echo=FALSE, warning=FALSE}
ggplot(trend,aes(vp,playoff_chance))+geom_point()+xlab('Victory Points')+ylab('Playoff Percentage')+coord_cartesian(xlim=c(0,20),ylim=c(0,3))
```

***

<br>

## **Awards** {#anchor5}

#### *Owner Awards*
|Award   |2019   |2020   |
|---|---|---|
|Champion   |Trevor Corsello   |   |
|Runner-Up   | John Postlethwait  |   |
| 3rd Place  |Cole Nelsen   |   |
|4th Place   |Rapha Siordia   |   |
| Mr. Irrelevant  | Jake Leahy  |   |
|Regular Season MVP   | Cole Nelsen  |   |
|Benchwarmer   |Phil Klafta   |   |
|Multiple Sidepots   | Cole Nelsen, John Postlethwait, Maxx Wayne (2)  |   |
| Biggest Tweak  | Trevor Corsello  |   |
|Ghost   | Jake Leahy  |   |
|The Luck of the Irish   |Rapha Siordia   |   |
| The Black Cat  | Jake Leahy  |   |
| The 13 Award  | Maxx Wayne  |   |
|Longest Win Streak   |  Trevor Corsello (7) |   |
| Longest Lose Streak  | Phil Klafta and Trent Wheeler (9)  |   |
| Biggest Fan Award  | Trevor Corsello  |   |

#### *Player Awards*
|Award   |2019   |2020   |
|---|---|---|
|Gardner Minshew Award   |Deshaun Watson (Rapha Siordia)   |   |
|New Orleans Saints Award   |Aarons Jones(2) and Leonard Fournette(9) (Maxx Wayne)   |   |
|Megatron Award  |Kenny Golladay(5) and Julian Edelman(8) (Cole Nelsen)  |   |
|Zach Miller Award   |Travis Kelce (Cole Nelsen)  |   |
|Nick Kwiatkowski Award   |Darius Leonard (Maxx Wayne)   |   |
|Biggest Draft Steal  |Chris Godwin-$6 (John Postlethwait)   |   |
|Biggest Draft Bust  |Juju Smith-Schuster-$60 (Julian Hilpuesch)   |   |
<br>
Note: All Player Awards must be drafted and stay on your team for the whole season.

***

<br>

## **Scoring** {#anchor6}

```{r include=FALSE}
pass=c('Yards','TD','INT','2 Point Conversion',rep(' ',6))
rush=c('Yards','TD','2 Point Conversion',rep(' ',7))
rec=c('Yards','Reception','TD','2 Point Conversion',rep(' ',6))
misc=c('Fumble','Kickoff Return TD','Punt Return TD','Fumble Return TD','Interception Return TD','Block Return TD','2 Point Return','1pt Safety',rep(' ',2))
def=c('Solo Tackle','Assited Tackle','Sack','Blocked Kick','INT','Fumble Forced','Fumble Recovered','Safety','Stuff','Pass Defended')
pass_stat=c(.04,4,-2,2,rep(' ',6))
rush_stat=c(.1,6,2,rep(' ',7))
rec_stat=c(.1,.5,6,2,rep(' ',6))
misc_stat=c(-2,12,12,12,12,12,8,6,rep(' ',2))
def_stat=c(1,.5,4,8,8,8,6,8,4,4)

passe=data.frame(cbind(pass,pass_stat))
rushe=data.frame(cbind(rush,rush_stat))
rece=data.frame(cbind(rec,rec_stat))
misce=data.frame(cbind(misc,misc_stat))
defe=data.frame(cbind(def,def_stat))
all=data.frame(passe,rushe,rece,defe,misce)
```

```{r echo=FALSE}
knitr::kable(all,col.names=c('Passing Stats','Points','Rushing Stats','Points','Recieving Stats','Points','Defensive Stats','Points','Miscellaneous','Points'))
```

***

<br>

##  **History** {#anchor7}

### *All time Standings*
